Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-09-22 Paper/conc.tex
..

Additionally, the surrogates were assessed by comparing probability distributions (based on kernel density estimation)
for the ignition delay, constructed using surrogate predictions and model evaluations at the same set of 10$^4$
random samples. The PDFs based on model evaluations and the 1-dimensional surrogate from the perturbation-based
strategy were found to be almost identical. However, the PDF based on 1-dimensional surrogate from the
regression-based strategy although captured the modal estimate with reasonable accuracy, was observed to
under-estimate the uncertainty in the ignition delay. Mean estimates of the ignition delay using model evaluations
and predictions using the two surrogates at 10$^4$ samples were found to be in agreement. However, as expected, the
standard deviation, computed using predictions from the surrogate based on the regression-based strategy was
found to be accurate only upto the first significant digit. Moreover, it was observed that the activity scores,
computed using the regression-based strategy failed to capture the sensitivity towards the 
most important parameter, $E_{a,15}$. 
We attribute this discrepancy to two potential sources of numerical errors: (1) Regression-based approximation of the
gradient of the model output, and (2) Scatter in the corresponding SSP (see Figure~\ref{fig:hd}) leading to numerical
error incurred by the linear regression fit in this case. Hence, the regression-based approximation of the gradient 
of the model output although reduces computational effort, the present investigations clearly reveal a potential pitfall associated
with this approach. Therefore, this approach should only be preferred in situations involving intensive simulations, and 
where the focus is essentially on estimating the statistics of the QoI as opposed to a more detailed analysis such as
parametric sensitivity analysis.

>>>>

Additionally, the surrogates were assessed by comparing probability distributions (based on kernel density estimation)
for the ignition delay, constructed using surrogate predictions and model evaluations at the same set of 10$^4$
random samples. The PDFs based on model evaluations and the 1-dimensional surrogate from the perturbation-based
strategy were found to be almost identical. However, the PDF based on 1-dimensional surrogate from the
regression-based strategy although captured the modal estimate with reasonable accuracy, was observed to
under-estimate the uncertainty in the ignition delay. Mean estimates of the ignition delay using model evaluations
and predictions using the two surrogates at 10$^4$ samples were found to be in agreement. However, as expected, the
standard deviation, computed using predictions from the surrogate based on the regression-based strategy was
found to be accurate only upto the first significant digit. Moreover, it was observed that the activity scores,
computed using the regression-based strategy failed to capture the sensitivity towards the 
most important parameter, $E_{a,15}$. 
We attribute this discrepancy to two potential sources of numerical errors: (1) Regression-based approximation of the
gradient of the model output, and (2) Scatter in the corresponding SSP (see Figure~\ref{fig:hd}) leading to numerical
error incurred by the linear regression fit in this case. Hence, the regression-based approximation of the gradient 
of the model output although reduces computational effort, the present investigations clearly 
reveals potential pitfalls associated with this approach. More specifically:
\begin{itemize}
\item The desired statistics (e.g. mean and variance) of the QoI might not be approximated
to a desired level of accuracy.
\item The approach might fail to capture the sensitivity  of the QoI towards all inputs. 
\end{itemize}
Therefore, the regression-based approach should only be preferred in situations involving intensive simulations such that the perturbation-based methods are intractable, and the objective is
essentially on obtaining rough estimates of the statistics of the QoI as opposed to a more detailed analysis such as those involving
parametric sensitivity.
